Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-12-18 Arxiv/main.tex
update localsensitivity analysis

	\item The accuracy is improved by two ways: 1) calibrating noise to the sensitivity of a metric over distributions (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots). 2) Using a smooth upper bound on the local sensitivity and scale the noise to this smooth bound rather than global sensitivity, to improve the mechanism accuracy.

  \item A full proof on applying exponential mechanism to the smooth sensitivity is $(\epsilon, \delta)-$differential privacy is given in paper.

	\item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and efficiency.
\end{itemize}

>>>>

	\item We explored two ways to improve the accuracy: 1) calibrating noise to the sensitivity of a metric over distributions (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots). 2) Using a smooth upper bound on the local sensitivity and scale the noise to this smooth bound rather than global sensitivity, to improve the mechanism accuracy.

  \item A full proof on the newly designed mechanism is $(\epsilon, \delta)-$differential privacy is given in paper.

	\item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and privacy.
\end{itemize}
